\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-06 jss/article.tex
journal writing

\section[Method Check]{Method Check}

\subsection{Pseudo-data Generation Process}
\subsection{Unbiased Coverage Probability}
\subsection{Rao-Blackwellized Coverage Probability}
\section[Example]{Example}
\subsection[Known Prior Mean]{Known Prior Mean}
Using 10 hospital data with PR
\subsection[Unknown Prior Mean and No Covariate]{Unknown Prior Mean and No Covariate}
Using 8 school data with GR
\subsection[Unknown Prior Mean and One Covariate]{Unknown Prior Mean and One Covariate}
Using 18 baseball data with BR

@@

\section[Reference]{Reference}
Efron, B. and Morris, C. (1975). Data Analysis Using Stein's Estimator and its Generalizations. \emph{Journal of the American Statistical Association}. \textbf{70}. 311-319.
\\
Rubin, D. B. (1981). Estimation in parallel randomized
  experiments. \emph{Journal of Educational Statistics}. \textbf{6}. 377-401.
\\
Morris, C. and Tang, R. (2011). Estimating Random Effects via Adjustment for Density Maximization. \emph{Statistical Science}. \textbf{26}. 271-287.
\\
Morris, C. and Lysy, M. (2012). Shrinkage Estimation in Multilevel Normal Models. \emph{Statistical Science}. \textbf{27}. 115-134.
\\

>>>>

\section[Method Check]{Method Check}
Like the two sides of the same coin, checking a statistical model always comes with fitting a model. If a fitted model cannot pass a checking process, we usually go back to the fitting process and come back to checking process iteratively. In this sense, checking a fitted model is an interactive procedure for the model justification.
\\

There are two kinds of model justification process; one is a model check and the other is a method check. The model check is for the justification of a hierarchical modeling on a specific dataset. One possible question is, ``Can this dataset benefit from such a modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $(z_{j}\vert \beta, r)\sim\textrm{Negative-Binomial}$, for Poisson data to justify the second-level hierarchy. They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
\\

The other model justification process is the method check.
\subsection{Pseudo-data Generation Process}
\subsection{Unbiased Coverage Probability}
\subsection{Rao-Blackwellized Coverage Probability}
\section[Example]{Example}
\subsection[Known Prior Mean]{Known Prior Mean}
Using 10 hospital data with PR
\subsection[Unknown Prior Mean and No Covariate]{Unknown Prior Mean and No Covariate}
Using 8 school data with GR
\subsection[Unknown Prior Mean and One Covariate]{Unknown Prior Mean and One Covariate}
Using 18 baseball data with BR

@@

\section[Reference]{Reference}
Christiansen, C. and Morris, C. (1996). ``Fitting and Checking a Two-Level Poisson Model: Modeling Patient Mortality Rates in Heart Transplant Patients,'' in \emph{Bayesian Biostatistics}, eds. D. Berry and D. Stangl, New York: Marcel Dekker, pp. 467-561.
\\
Efron, B. and Morris, C. (1975). ``Data Analysis Using Stein's Estimator and its Generalizations.'' \emph{Journal of the American Statistical Association}. \textbf{70}. 311-319.
\\
Morris, C. and Tang, R. (2011). ``Estimating Random Effects via Adjustment for Density Maximization.'' \emph{Statistical Science}. \textbf{26}. 271-287.
\\
Morris, C. and Lysy, M. (2012). ``Shrinkage Estimation in Multilevel Normal Models.'' \emph{Statistical Science}. \textbf{27}. 115-134.
\\
Rubin, D. B. (1981). ``Estimation in parallel randomized
  experiments.'' \emph{Journal of Educational Statistics}. \textbf{6}. 377-401.
\\
